---
title: "R Notebook"
output: html_notebook
---



Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

### Install package and check the dataset
install.packages(nycflights13)
help(flights)

```{r echo=TRUE}
library(nycflights13)
fligths<-nycflights13::flights
head(fligths)
```


###  Que arribaron con un retraso de mas de dos horas.

```{r}
subset(fligths, arr_delay > 120)
```

### Los vuelos que volaron hacia Houston (IAH o HOU)
```{r}
subset(fligths, dest == "IAH" | dest == "HOU")
```
## Los vuelos operados por United "UA", American "AA" o Delta "DL".
```{r}
airlines<-nycflights13::airlines
airlines
subset(fligths, carrier == "UA" | carrier == "DL" | carrier == "AA")
```


## Salieron en Verano (Julio, Agosto y Septiembre)
```{r}
subset(fligths, month >= 7 & month  <= 9 )
```

## Arrivaron mas de dos horas tarde, pero salieron bien.
```{r}
subset(fligths, arr_delay > 120 & dep_delay == 0)
```
## Salieron entre medianoche y las 6 am.
```{r}
subset(fligths, dep_time < 600)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
